Halo alignments with large scale tidal and velocity fields

### 2013-02-27 paper/main.tex
new references

\citep{Libeskind2013} %various alignments
\citep{Codis2012}
\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

\begin{itemize}
\item
\citep{AragonCalvo2007} %Spin alignment
The method is the Multi-scale Morphology Filter which is based on the
Hessian matrix of the density field, where the density field is
computed from the particle distribution using a Delaunay tesselation
field estimatior (DTFE), which is self-adaptive. This allows them to
identify clusters, filaments and walls.

@@

They do not see any strong dependance of the environment in the
shape. They do not measure the shape alinment.

\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for mutual alignment of angular momentum vectors, and
alignment with structure. halos on any escale by close pair
statistics. They don't find any evidence for a statistically significant mutual
alignment of haloes on any scale,
\end{itemize}
\section{N-body simulation and halo finding}

>>>>

\citep{Libeskind2013} %various alignments

\citep{Faltenbacher2009} %galaxy alignments with mocks
\citep{Paz2008} %angular momentum alignments
\citep{Platen2008} %alignment in voids
\citep{Lee2007}%Obs. spin alignment

\begin{itemize}
\item 
\citep{Codis2012}
Studies the alignment of the sping of dark matter halos realtive to
the surrounding large scale structure and to the tidal tensor
eigenvalues.

They use a dark matter simulation with $4096^3$ DM particles in a
cubic periodic box of $2000$\hMpc on a side, which corresponds to a
particle mass of $7.7\times 10^9$\Msun. Halos are identified
using a FoF algorithm with a linking legth of 0.2 keeping all halos
with more than 40 particles, which sets the minimum halo mass to be
$3\times 10^{11}$\Msun. In their work the particles were sampled on a
$2048^3$ grid and the density field was smoothed with a gaussian
fileter over a scale of $5$\hMpc corresponding to a mass of $1.9\times
10^{14}$. The skeleton was computed over $6^{3}$ overlapping subcubes
and then reconnected.

The filament finder algorithm is based on Morse theory and defines a
Skeleton to be the set of critical lines joining the maxima of the
densit field through saddle points following the gradient. They also
compute the hessinan of the potential over the smoothed density field
to get their eigenvectors.

The spin of the halo is defined as $m_{p}\sum_{i}(r_i-\bar{r})\times
(v_i-\bar{v})$ where $\bar{r}$ is the center of mass of the halo and
$\bar{v}$ is the average velocity.

They measure the sping alignment with each one of the
eigenvectors. With repecto to the first eigenvector $e_{1}$ there is
antialignement for masses $M>10^{12}$\Msun and alignment for masses
$<10^{12}$\Msun

\item 
\citep{AragonCalvo2007} %Spin alignment
The method is the Multi-scale Morphology Filter which is based on the
Hessian matrix of the density field, where the density field is
computed from the particle distribution using a Delaunay tesselation
field estimatior (DTFE), which is self-adaptive. This allows them to
identify clusters, filaments and walls.

@@

They do not see any strong dependance of the environment in the
shape. They do not measure the shape alinment.
\item
\citep{Basilakos2006}
Use a cosmological SPH+N-body simulation to measure the alignment of
cluster halos with their parent supercluster. For both the cluster
halos and parent super-cluster they define the shape via the
non-normalized inertia tensor.  The find that strenght of the
alignments increases with the degree of filamentarity of the
supercluster.

The simulation has $2\times 512^3$ particles in a box of side
$500$\hMpc. The dark matter particle mass is $6.6\times
10^{10}$\hMsun while for SPH particles is $1.2\times
10^{10}$\hMsun. The halo finding is done with a FOF algorithm with a
linking length of 0.17 and keep objects with more than 100 partcles.

\item
\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for mutual alignment of angular momentum vectors, and
alignment with structure. halos on any escale by close pair
statistics. They don't find any evidence for a statistically significant mutual
alignment of haloes on any scale,
\end{itemize}
\section{N-body simulation and halo finding}
